---
title: "Random forest regression"
author: "Vi-n1"
output:
  html_document: default
---

# Installing and loading libs

```{r, message=FALSE}
if(!require("tidyverse")) install.packages("tidyverse", repos = "https://cloud.r-project.org")
if(!require("randomForest")) install.packages("randomForest", repos = "https://cloud.r-project.org")
if(!require("car")) install.packages("car", repos = "https://cloud.r-project.org")
```

```{r, message=FALSE}
library(tidyverse)
library(randomForest)
library(car)
```

# Data import

```{r, warning=FALSE}
dt = readr::read_csv("database/realest.csv")
```

# Data cleaning

***The choice was to delete missing data***

```{r}
# Amount of missing information and total row in the database
cbind(na = sum(is.na(dt)), rows = nrow(dt))
```

```{r}
dt <- dt %>% drop_na()
# Number of lines removed
cbind(na = sum(is.na(dt)), rows = nrow(dt))
```

# Normality test

```{r}
# Significance level
SIG <- 0.05

list_names <- names(dt)

# Teste de Shapiro-Wilk 
for (name in list_names){
  result <- 
    dt[,name] %>%
    unlist() %>%
    as.numeric() %>%
    shapiro.test()
  if(result[2] > SIG){str_c(name , " = Normally distributed")}
  else{str_c(name , " = Not normally distributed")} %>%
  print()
}
rm(SIG)
rm(list_names)
rm(result)
rm(name)
```

# Graphic normality test

```{r}
qqPlot(dt$Price, dist='norm',envelope=.95)
qqPlot(dt$Space, dist='norm',envelope=.95)
qqPlot(dt$Tax, dist='norm',envelope=.95)
```

# Correlation Test

```{r}
for (i in c(2:length(dt))){
  correlation <- cor(y = dt$Price, x = dt[,i], method = "spearman")
  print(str_c(names(dt[,i]), " = ",correlation))
}
rm(i)
rm(correlation)
```

```{r, message=FALSE}
# Separating the model variables
dt <- dt[,c("Space", "Tax", "Price")]

# make it reproducible
set.seed(1)

# Separating 70% for training and 30% for testing
train <- dt %>% sample_frac(0.70)
test  <- anti_join(dt, train)
```

# Random Forest regression

```{r}
# make it reproducible
set.seed(1)

model = randomForest(
  formula = Price ~ .,
  data = train,
  ntree=800,
  nodesize = 3,
  keep.forest= TRUE, 
  random_state = 0,
  xtest = test[,1:2],
  ytest = test$Price
  )
model
```

# Validating the random forest regression model

## Assumptions for the Random Forest Algorithm:

-   Absence of multicollinearity;

-   Identical distribution.

```{r}
# checking multicollinearity
cor(dt$Space, dt$Tax, method = "spearman")
```

### Result: They all follow the same distribution, there is a low correlation, but the model remains valid.

Database source link: <https://www.kaggle.com/datasets/tawfikelmetwally/chicago-house-price/>
